Headgroup structure and cation binding in phosphatidylserine lipid bilayers

### 2019-06-26 Manuscript/manuscriptPS.tex
Move table a bit

@@

POPC:POPS (5:1)/Na$^{+}$  & GROMOS-CKP$^*$ \cite{piggot12}  & 0  & 110 & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \citenum{POPCpopsGROMOSCKPwithNa} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & GROMOS-CKPM$^*$ \cite{piggot12}  & 0  & 110 & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \citenum{POPCpopsGROMOSCKPMwithNa} \tabularnewline

>>>>

\vspace{1cm}

@@

POPC:POPS (5:1)/Na$^{+}$  & GROMOS-CKP\footnote{Force field parameters for PS lipids generated for this work, for full details see the supplementary information.} \cite{piggot12}  & 0  & 110 & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \citenum{POPCpopsGROMOSCKPwithNa} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & GROMOS-CKPM$^c$ \cite{piggot12}  & 0  & 110 & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \citenum{POPCpopsGROMOSCKPMwithNa} \tabularnewline
